The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-03-26 tbl-alternativeinternet.tex
Table column alignment, so they all fit on one row
Center table headers

\begin{tabular}[p]{| r | l | p{2.2cm} | p{1.2cm} | p{2.2cm} | p{1.2cm} | p{1.5cm} | p{2.3cm} |}
	\hline
	\textbf{\#} & \textbf{Name} & \textbf{Language} & \textbf{Age} & \textbf{Last activity} & \textbf{LOC} & \textbf{Commits} & \textbf{Contributors} \\ \hline

>>>>

\begin{tabular}[p]{| r | l | p{1.5cm} | r | r | r | r | r |}
	\hline
	\tblhead{\#} & \tblhead{Name} & \tblhead{Language} & \tblhead{Age} & \tblhead{Last activity} & \tblhead{LOC} & \tblhead{Commits} & \tblhead{Contributors} \\ \hline
